How single mutations affect viral escape from broad and narrow antibodies to H1 influenza hemagglutinin

### 2018-02-22 paper/manuscript.tex
added cover letter and a few more tweaks

\begin{suppdata}
\caption{\label{suppdata:analysis_code}
{\bf Computer code and data for the analysis of the mutational antigenic profiling data.}
The code in this ZIP file performs the entire computational analysis beginning with downloading the FASTQ files from the Sequence Read Archive.
The ZIP file contains a \texttt{README} file that explains the contents in detail.
The actual analysis is performed by the Jupyter notebook \texttt{analysis\_notebook.ipynb}, which includes embedded plots summarizing key statistics and results.
An HTML version of this notebook is also included as Supplementary Data~\ref{suppdata:analysis_code}.
}
\end{suppdata}

@@

\begin{suppdata}
\caption{\label{suppdata:fracsurvive}
{\bf The fraction surviving for each mutation for each antibody.}
This file differs from File~\ref{suppdata:fracsurvive_excess} only in that the values are \emph{not} adjusted to be in excess of the library average (e.g., they are from Equation~\ref{eq:fracsurvive} rather than Equation~\ref{eq:fracsurvive_excess}).
}
\end{suppdata}

>>>>

\begin{suppdata}
\caption{\label{suppdata:analysis_code}
{\bf Computer code and data for the analysis of the mutational antigenic profiling data.}
The code in this ZIP file performs the entire computational analysis beginning with downloading the FASTQ files from the Sequence Read Archive.
The ZIP file contains a \texttt{README} file that explains the contents in detail.
The actual analysis is performed by the Jupyter notebook \texttt{analysis\_notebook.ipynb}, which includes embedded plots summarizing key statistics and results.
An HTML version of this notebook is also included as Supplementary Data~\ref{suppdata:analysis_html}.
}
\end{suppdata}

@@

\begin{suppdata}
\caption{\label{suppdata:fracsurvive}
{\bf The fraction surviving for each mutation for each antibody.}
This file differs from Supplementary Data~\ref{suppdata:fracsurvive_excess} only in that the values are \emph{not} adjusted to be in excess of the library average (e.g., they are from Equation~\ref{eq:fracsurvive} rather than Equation~\ref{eq:fracsurvive_excess}).
}
\end{suppdata}
